---
title: "civicfeedR: Getting News From CivicFeed"
author: "Santoshi G"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{civicfeedR: Getting News From CivicFeed}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  eval = FALSE
)
library(civicfeedR)
library(dplyr)
```

This vignette provides an overview of the `civicfeedR` package, which can be used to retrieve and restructure data from the CivicFeed News API.

## Looking up source IDs

If you're interested in exploring news from specific sources, use `lookup_id` to find source IDs.

```{r}
## look up IDs of news sources of interest using keywords
bbc = lookup_id("bbc")
nyt = lookup_id("new york times")

## inspect relevant results
bbc
nyt

## store IDs of news sources of interest 
sources = c(bbc[[1]], nyt[[7]])
```

## Getting the news

To retrieve news data, make API requests using `get_news`.

```{r}
## check number of results corresponding to desired queries, if necessary
results(q = "congress", sources = sources, from = "2018-12-01")

## get 30 most popular bbc/nyt articles posted after 2018-12-01 and corresponding to query "congress" 
popular = get_news(
  q = "congress", 
  sources = sources, 
  from = "2018-12-01", 
  sort = "socialcount_last"
)

## get 30 bbc/nyt articles posted after 2018-12-01 and most relevant to query "congress" 
relevant = get_news(
  q = "congress", 
  sources = sources, 
  from = "2018-12-01", 
  sort = "_score"
  )
```

## Creating a dataset

Using the `from` family of functions, create your own dataset from the data retrieved.

```{r}
## create a tibble of titles from "popular" and "relevant"
titles = titles_from(popular, relevant)

## create a tibble of snippets from "popular" and "relevant"
snippets = snippets_from(popular, relevant)

## combine the tibbles by article_id
df = dplyr::full_join(titles, snippets, by = "article_id")
df
```

## Studying specific entities

If you're interested in the news coverage of specific entities, take advantage of the `mentioned` function.

```{r}
## inspect names of entities of interest in "popular" and "relevant"
entities_from(popular, relevant)

## get titles, dates published and social media shares from popular and relevant articles abot congress mentioning nancy pelosi and chuck schumer
mentioned(popular, relevant, entities = c("nancy pelosi", "chuck schumer"), shares = TRUE)
```

